---
title: 'Salma Elshahawy: CV'
output:
  html_document:
    css: ["css/make-cv-like-other.css", "css/one-column-cv.css", "css/website-page.css", "css/style.css", "fontawesome-free-5.8.1-web/css/all.min.css"]
    toc: true
    toc_float: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)

#### projects #####
projects <- readxl::read_xlsx("_cv_data/projects.xlsx")

#### all other entries #####
cv_entries <- readxl::read_xlsx("_cv_data/cv_entries.xlsx")

```

<br>

# Summary

**_Implementing data-driven, action-oriented solutions to challenging business problems_**

I am a business-minded data scientist with demonstrated skills to infer worthy insights through data analytics and exceptional statistical predictive models. I am a proficient problem solver with more than two years of experience in software engineering within the financial and healthcare industries.

I am also a full-stack Software Engineer with a passion for cleanly written, organized, and well-tested code. I have an extraordinary passion for **Python** as a data _analysis language_.

I have experience using Javascript, Ruby, R, Java, and their frameworks. I’ve developed many applications in many languages, especially in the financial industry. My background in mechanical engineering helped me to improve my capabilities as a Software Engineer within healthcare and financial industries.

I like to learn by reading and to convey the learning skills via writing. I have a blogpost on [Medium](https://medium.com/@salmaeng71) - Kindly check it out. Many followers find it useful to them.


You can download a brief version of [my Resume as PDF](https://github.com/salma71/resume_website/blob/master/Salma-Resume_June10.pdf).

<br>


## Skills {.technical .nohead}
```{r}
cv_entries %>% 
  filter(type == 'technical') %>% 
  mutate(what = str_c("- **", what, ":** ", additional_info)) %>% 
  select(what) %>% 
  kable()
```



## Selected work experience
```{r}
cv_entries %>% 
  filter(type == 'work', is.na(website)) %>% 
  mutate(additional_info = replace_na(additional_info, "")) %>% 
  mutate(what = str_c("<span class='work-title'>", what, "</span><br class='work-break'>", where, "<br>", "</span><br class='work-break'>", additional_info)) %>% 
  arrange(desc(year_begin)) %>% 
  mutate(year = ifelse(!is.na(year_end), str_c(year_begin, " --- ", year_end), year_begin)) %>% 
  select(year, what) %>% 
  kable()
```


## Education {.education .nohead}
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = str_c(what, ", ", where)) %>% 
  mutate(year = str_c(year_begin, " --- ", year_end)) %>% 
  select(year, what) %>% 
  kable()
```

## Projects {.tabset .nohead .publications .tabset-fade}

### Data science
```{r}
projects %>%
  filter(type == "data science") %>%
  mutate(title = ifelse(!is.na(url), str_c("<span class='work-title'>","[", title, "](", url, ")", "</span><br class='work-break'>",  "<br>", "</span><br class='work-break'>"), title)) %>% #turn title into link
  mutate(GitHub = ifelse(!is.na(GitHub), str_c("[GitHub-Repo](", GitHub, ")"), GitHub)) %>%
  select(title, short_title, GitHub, stack) %>%
  #mutate(title = str_c("<span style='text-decoration: underline'>", title, "</span>")) %>% #underline title

knitr::kable()
```

### Web development
```{r}
projects %>%
  filter(type == "web development") %>%
  mutate(title = ifelse(!is.na(url), str_c("<span class='work-title'>","[", title, "](", url, ")", "</span><br class='work-break'>",  "<br>", "</span><br class='work-break'>"), title)) %>% #turn title into link
  mutate(GitHub = ifelse(!is.na(GitHub), str_c("[GitHub-Repo](", GitHub, ")"), GitHub)) %>%
  select(title, short_title, GitHub, stack) %>%
  #mutate(title = str_c("<span style='text-decoration: underline'>", title, "</span>")) %>% #underline title

knitr::kable()
```





^[This website is done by R-markdown and pagedown package using R]
